Seasonality in governing submesoscale dynamics in the Kuroshio Extension

### 2016-07-04 writeup/rocha_etal.tex
Minor edit

Our work adds to recent studies that presented modeling \citep{sasaki_etal2014}
and observational \citep{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. We conjecture that the summertime dominance of inertia-gravity waves
 \citep{callies_etal2015} is a consequence both of suppression of submesoscale turbulence and
enhancement of inertia-gravity waves due to re-stratification of
the upper ocean. Of course, this study focuses on a single patch of ocean in the
vicinity of the Kuroshio Extension, which may be typical of mesoscale-rich
subtropical regions, but is unlikely to be
representative of other regions such as low eddy kinetic energy eastern boundary currents
and the middle of the subtropical gyre; care must be taken to avoid overgeneralizing
these results.  We plan to report on the geographic variability of submesoscale
 seasonality in a future study.

>>>>

Our work adds to recent studies that presented modeling \citep{sasaki_etal2014}
and observational \citep{callies_etal2015,buckingham_etal2016} evidence of vigorous seasonality in
submesoscale turbulence. We conjecture that the summertime dominance of inertia-gravity waves
 \citep{callies_etal2015} is a consequence both of suppression of submesoscale turbulence and
enhancement of inertia-gravity waves due to re-stratification of
the upper ocean. Of course, this study focuses on a single patch of ocean in the
vicinity of the Kuroshio Extension, which may be typical of mesoscale-rich
subtropical regions, but is unlikely to be
representative of other regions such as low eddy kinetic energy eastern boundary currents
and the middle of the subtropical gyre.  We plan to report on the geographic variability of submesoscale
 seasonality in a future study.
